Online {\IterComp}

### 2017-09-14 results.tex
arrrrrrrrrrrrrrrrrrrrrrrrrrrrrrrgh

In this section we discuss our experimental evaluation.
First we describe the benchmarks with datasets used in the experiments.
Afterwards, we discuss our results concerning the instrumentations for profiling our work metric.
Finally we present the results of the online {\itercomp}.

@@

We first compare static aspects of the instrumentation algorithms.
The naive instrumentation always has 100\% of the basic blocks instrumented, by definition.
First, we evaluate the optimal work profiling compared to the relaxation algorithm applied per DAG.
Afterwards, we compare these profiling techniques with the whole program relaxation.

>>>>

%In this section we discuss our experimental evaluation. Afterwards, we discuss our results concerning the instrumentations for profiling
%our work metric. Finally we present the results of the online {\itercomp}.

@@

We first compare static aspects of the instrumentation algorithms. The naive instrumentation instrument all basic blocks, by definition.
First, we evaluate the optimal work profiling compared to the relaxation algorithm applied per DAG. Afterwards, we compare these profiling
techniques with the whole program relaxation.

### 2017-09-14 work.tex
arrrrrrrrrrrrrrrrrrrrrrrrrrrrrrrgh

Similarly to previous work~\citep{giusto01,powell09,brandolese11}, we derive the cost model of the instruction set by modelling the problem as a multi-variable linear regression, where the \textit{regression coefficients} are the costs of the instructions and the \textit{regressors} are computed as $\sum_B N_B(i)f(B)$ for each instruction.
\begin{equation}\label{eq:linear-work-expression}
\Delta W = \varepsilon + \sum_{i} \left(w_i \sum_{B} N_B(i)f(B)\right)
\end{equation}
By having some empirical data after executing several benchmarks with different inputs, we can fit the linear model with this empirical data in order to obtain estimate costs of the instructions.
In order to fit the linear model, we measure the wall-clock time when executing the training benchmarks described in Section\ref{sec:benchmarks} with their respective 1000 input datasets.
For these measurements, the training benchmarks are compiled without optimization.
The reason for using no optimization, as discussed in Section\ref{sec:oic-infra}, is because the amount of work must be only input dependent and consistent between different optimization sequences.
This aspect is crucial for the work-based performance metric to enable a consistent comparison between the various optimization sequences when executing with distinct inputs.
%it allows to use the estimated cost model for computing a work metric which is independent of optimizations, as we explained in Section~\ref{}.

>>>>

Similarly to previous work~\citep{giusto01,powell09,brandolese11}, we derive the cost model of the instruction set by modeling the problem
as a multi-variable linear regression. The \textit{regression coefficients} are the costs of the instructions and the \textit{regressors}
are computed as $\sum_B N_B(i)f(B)$ for each instruction.
\begin{equation}\label{eq:linear-work-expression}
\Delta W = \varepsilon + \sum_{i} \left(w_i \sum_{B} N_B(i)f(B)\right)
\end{equation}

We use a set of training programs to construct the regression model. Our training program set is given in
Table~\ref{tab:kdatasets:training}. To determine the model coefficients, we profile each training benchmark with 1000 input datasets
provided by the benchmark suite, and we measure the wall-clock time. It is to note that we turn off all compiler optimisations during this
training stage, to ensure that the amount of work we measured only depends on the program input but not compiler optimization. This aspect
is crucial for the work-based performance metric to allow a consistent comparison between the various optimization sequences when executing
with distinct inputs.

%it allows to use the estimated cost model for computing a work metric which is independent of optimizations, as we explained in Section~\ref{}.
